Improving \textsl{Gaia} parallax precision \\ with a data-driven model of stars

### 2017-06-14 paper/paper.tex
bias

LMA: describe Figure \ref{fig:deltaParallax}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{deltaParallax.pdf}
\caption{The difference between the expectation value of our parallax posteriors and the \gaia\ parallax measurement as a function of the \gaia\ uncertainty. The points are colored by the fractional change in the variance of the posterior PDF compared with the \gaia\ likelihood, the same as Figure \ref{fig:delta}. The points are evenly distributed around $y=0$ showing that there is little bias in our inferred parallax PDFs. The distribution gets wider with larger \gaia\ uncertainties due to those lower signal to noise measurements being more influenced by the prior. They also tend to have the largest fractional change in their variance (shown as darker points)}
\label{fig:deltaParallax}
\end{figure}

>>>>

We have shown that the posterior parallax estimates are more precise
than the likelihoods, both on average and especially for low
signal-to-noise stars.
It is also interesting to ask whether our data-driven prior leads to
biased inferences.
In Figure~\ref{fig:deltaParallax}, we show the shifts of the parallax
estimates from likelihood \tgas\ catalog entry to posterior
expectation.
This shows that while many parallax estimates change substantially,
they do not change on average, even at low signal-to-noise ratios.
Our conclusion is that the prior developed here does not introduce additional
bias into the \tgas\ parallax measurements.

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{deltaParallax.pdf}
\caption{The difference between the expectation value of our parallax posteriors and the \gaia\ parallax measurement as a function of the \gaia\ uncertainty. The points are colored by the fractional change in the variance of the posterior PDF compared with the \gaia\ likelihood, the same as Figure \ref{fig:delta}. The points are evenly distributed around $y=0$ showing that there is little bias introduced by inferred parallax PDFs. The distribution gets wider with larger \gaia\ uncertainties due to those lower signal to noise measurements being more influenced by the prior. They also tend to have the largest fractional change in their variance (shown as darker points)}
\label{fig:deltaParallax}
\end{figure}
